Supplementary Information

### 2020-12-21 doc/manuscript/MEE_manuscript_SI.Rmd
update SI

climwin_sameV_sameW_legend = "Figure S5. (PRE at SCBI)"
climwin_sameV_diffW_legend = "Figure S6. (PET at SCBI)"
climwin_diffV_diffW_legend = "Figure S7. (PRE/WET at Harvard Forest)"

@@

\newpage
## `r species_table_legend` 
*([ISSUE #72 in ForestGEO-climate-sensitivity ](https://github.com/EcoClimLab/ForestGEO-climate-sensitivity/issues/72))*

```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
S2 <- read.csv("tables_figures/species.csv", col.names = c("species code", "family","latin name", "sites sampled", "leaf type", "leaf phenology", "light requirements", "bark allometry*"), stringsAsFactors = FALSE, check.names = FALSE)
kable(S2, format = "latex", booktabs = TRUE,  escape = F, linesep = c('\\addlinespace'))%>%
  row_spec(0, italic = F, bold = T) %>%
  column_spec(8, width = "5cm") %>%
  kable_styling(latex_options = c("scale_down", "hold_position")) 
```
*Bark allometry field indicates the species and site sampled to construct the bark allometry. When neither raw data nor an allometric equation for the study species was available, we selected the most appropriate equation that could be located for similar species. Equations are given in Table `r bark_allometries`.

@@

\newpage
## `r climwin_diffV_diffW_legend`
![](tables_figures/SI_figures/climwin_plots_combined/HarvardForest_pre_wet.png)

>>>>

climwin_sameV_sameW_legend = "Figure S5. (PRE at SCBI)"
climwin_sameV_diffW_legend = "Figure S6. (PET at SCBI)"
climwin_diffV_diffW_legend = "Figure S7. (TMX/TMP at HKK)"

@@

\newpage
## `r species_table_legend`

```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
S2 <- read.csv("tables_figures/species.csv", col.names = c("species code", "family","latin name", "sites sampled", "leaf type", "leaf phenology", "light requirements", "bark allometry*"), stringsAsFactors = FALSE, check.names = FALSE)
kable(S2, format = "latex", booktabs = TRUE,  escape = F, linesep = c('\\addlinespace'))%>%
  row_spec(0, italic = F, bold = T) %>%
  column_spec(8, width = "5cm") %>%
  column_spec(3, italic = T) %>%
  column_spec(8, italic = T) %>%
  kable_styling(latex_options = c("scale_down", "hold_position")) 
```
*Bark allometry field indicates the species and site sampled to construct the bark allometry. When neither raw data nor an allometric equation for the study species was available, we selected the most appropriate equation that could be located for similar species. Equations are given in Table `r bark_allometries`.

@@

\newpage
## `r climwin_diffV_diffW_legend`
![](tables_figures/SI_figures/climwin_plots_combined/HKK_tmp_tmx.png)
